`r paste(params$file_path, ' ', params$intervention, ' Handover Plots')`

### 2024-01-22 minos/outcomes/CPR_vis.Rmd

```{r read_data}
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'scaled_scotland')

@@

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_whole_pop_single.png')

    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}

@@

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_whole_pop_batch.png')
    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}
```

@@

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_families_single.png')

    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}

@@

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_families_batch.png')
    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}
```

@@

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_treated_single.png')
    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}

@@

  if (shall.we.save) {
    filename <- paste0(save.path, 'SF12_treated_single.png')
    ggsave(filename = filename,
           plot = p1,
           width = plot.width,
           height = plot.height)
  }
}
```

@@

  if (batch) {
    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
      geom_smooth() +
      geom_hline(yintercept = 0, linetype='dashed') +
      facet_wrap(. ~ scen, ncol=1) +
      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
      xlab('Year') +
      ylab('Difference')
  } else {
    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
      geom_line() +
      geom_hline(yintercept = 0, linetype='dashed') +
      facet_wrap(. ~ scen, ncol=1) +
      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
      xlab('Year') +
      ylab('Difference')
  }

  ggsave(filename = 'test_plot.png',
         plot = p1,
         path = here::here('plots', 'SCOTGOVWORK'),
         width = 9,
         height = 20)

>>>>

```{r read_data}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'scaled_scotland')
out.path <- here::here('output', 'default_config_batch')

@@

  # if (shall.we.save) {
  #   filename <- paste0(save.path, 'SF12_whole_pop_single.png')
  # 
  #   ggsave(filename = filename,
  #          plot = p1,
  #          width = plot.width,
  #          height = plot.height)
  # }
}

@@

  # if (shall.we.save) {
  #   filename <- paste0(save.path, 'SF12_whole_pop_batch.png')
  #   ggsave(filename = filename,
  #          plot = p1,
  #          width = plot.width,
  #          height = plot.height)
  # }
}
```

@@

  # if (shall.we.save) {
  #   filename <- paste0(save.path, 'SF12_families_single.png')
  # 
  #   ggsave(filename = filename,
  #          plot = p1,
  #          width = plot.width,
  #          height = plot.height)
  # }
}

@@

  # if (shall.we.save) {
  #   filename <- paste0(save.path, 'SF12_families_batch.png')
  #   ggsave(filename = filename,
  #          plot = p1,
  #          width = plot.width,
  #          height = plot.height)
  # }
}
```

@@

  # if (shall.we.save) {
  #   filename <- paste0(save.path, 'SF12_treated_single.png')
  #   ggsave(filename = filename,
  #          plot = p1,
  #          width = plot.width,
  #          height = plot.height)
  # }
}

@@

  # if (shall.we.save) {
  #   filename <- paste0(save.path, 'SF12_treated_single.png')
  #   ggsave(filename = filename,
  #          plot = p1,
  #          width = plot.width,
  #          height = plot.height)
  # }
}
```

@@

  if (batch) {
    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
      geom_smooth() +
      geom_hline(yintercept = 0, linetype='dashed') +
      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
      xlab('Year') +
      ylab('Difference')
  } else {
    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
      geom_line() +
      geom_hline(yintercept = 0, linetype='dashed') +
      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
      xlab('Year') +
      ylab('Difference')
  }

  # ggsave(filename = 'test_plot.png',
  #        plot = p1,
  #        path = here::here('plots', 'SCOTGOVWORK'),
  #        width = 9,
  #        height = 20)

### 2024-01-22 minos/outcomes/SCP_vis.Rmd

# define subset of variables to reduce size of batch output
var.list <- c('pidp', 'hidp', 'time', 'weight', 
              'age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
              'hh_income', 'child_ages', 'simd_decile',
              'SF_12', 'matdep_child')

@@

#int.list <- c(int25, int30, int35, int40, int45, int50)
int.list <- list(base, int25, int30, int35, int40, int45, int50)
scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')

@@

# Save path and save flag
save.path <- here::here('plots', 'SCOTGOV', 'CPR')
create.if.not.exists(save.path)
shall.we.save <- FALSE
plot.width <- 10
plot.height <- 5
```

>>>>

# define subset of variables to reduce size of batch output
var.list <- c('age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
              'hh_income', 'child_ages', 'simd_decile',
              'SF_12', 'matdep_child')

@@

#int.list <- c(int25, int30, int35, int40, int45, int50)
# int.list <- list(base, int25, int30, int35, int40, int45, int50)
# scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')

int.list <- list(base, int25, int50)
scen.list <- c('base', 'int25', 'int50')

@@

# Save path and save flag
save.path <- here::here('plots', 'SCOTGOVWORK', 'CPR')
create.if.not.exists(save.path)
shall.we.save <- FALSE
plot.width <- 10
plot.height <- 5
```

### 2024-01-22 minos/validation/cross_validation_default.Rmd

## Job Sec

```{r}
jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'job_sec')

cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
                 var = 'job_sec',
                 save = FALSE)
rm(jobsec.pivoted)
```

## Hourly Wage

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
multi_year_boxplots(raw, cv, 'hourly_wage')
q_q_comparison(raw, cv, 'hourly_wage')
```

@@

>>>>

%## Job Sec
%
%```{r}
%jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
%                                          df1.name = 'simulated', 
%                                          df2 = raw, 
%                                          df2.name = 'raw', 
%                                          var = 'job_sec')
%
%cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
%                 var = 'job_sec',
%                 save = FALSE)
%rm(jobsec.pivoted)
%```
%
%## Hourly Wage
%
%```{r}
%cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
%multi_year_boxplots(raw, cv, 'hourly_wage')
%q_q_comparison(raw, cv, 'hourly_wage')
%```

@@

## CHILDREN AGEING

### 2024-01-22 minos/validation/handovers.Rmd

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)

#

#out.path <- here::here('output', 'scotland_scaled/')
#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)

# HR 283-285 older version (285)
# out.path <- here::here('output', 'child_poverty_config/')
# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
```

@@

## Child Ages

>>>>

```{r}

file_path <- params$file_path
intervention <- params$intervention

# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

#out.path <- here::here('output', 'default_config/')
#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)

out.path <- here::here('output', file_path)
base.dat <- read_singular_local_out(out.path, intervention, drop.dead = TRUE)
```

@@
